### 2014-03-01 thesis/src/chapters/chapter-design.tex
Thesis: refinements

\section{Overview}
The previous section dealt with all premises that led to a conclusion that the proposed architecture can rely heavily on the concept of an autonomic system. In this section the further elaboration on the solution is presented.
Figure \ref{img:csap-usage-context} showed the context which the architecture applies to. As one can see, Cloud-SAP can be seen as a proxy between the user and cloud instances and as a coordinator of the latter. Although cloud instance itself consists of a cloud manager and additional resources, in general, it is perfectly legitimate to consider it a resource as well.

@@

Each autonomic manager implements the control loop which can be split into four consecutive blocks, which share knowledge among one another. The output from one block forms an input to another. However, it is perfectly possible for a block to perform an action for its side effects, e.g. an action can result in producing relevant information contained in log files, which, in turn, comprises a piece of shared knowledge. Each block implements different behaviour based on the abstraction level and resource they operate on (see figure \ref{img:csap-layered-structure}). Nevertheless it is possible to define their generic behaviour, which embraces the four phases: monitoring, analysis, planning, execution.

@@

\subsection{Structure}
It is clear from the description of requirements of this autonomic manager in the previous section that \emph{plan} and \emph{execution} functions are common for both of them. Therefore the \emph{cloud federation manager} is composed of two internal autonomic managers, which perform complete different functions, the first one -- \emph{monitor} and \emph{analyse} and the second -- \emph{plan} and \emph{execute}, yet they cooperate with each other to realize the full control loop.

@@

\begin{asparaenum}
  \item[\textbf{Problem description}]
The problem of resource management in cloud computing environments is hard and complex. This is because of several aspects. The first one is the characteristic of resources available in a cloud -- not only are they geographically distributed, but they can be under different administrative domains and can vary in accessibility. This places a heavy burden on cooperation possibilities across cloud providers, both in a technical and non-technical way as providers need to maintain the high level of trust in order to effectively  deliver its products. Additionally, different entities forms the resources -- starting from individual devices, through virtual machines and whole workstations, ending with clusters and data centers. The second one are the increasing Quality-of-Service requirements from the clients. They want resources they use to be reliable, flexible (able to scale according to workload), fault-tolerant, energy-efficient and, of course, cheap. It is clear that clients and cloud vendors have different objectives and supply-and-demand patterns.

@@

  \begin{asparaenum}
  \item[\textbf{Service deployment}] When the user wants to deploy a service on a cloud infrastructure, they have to prepare its detailed description containing technical (stacks) and Quality-of-Service requirements.
  \item[\textbf{Service scaling}] When an application needs to be scaled, there is available additional knowledge that this component should use of -- detailed information about service's performance up to that point, e.g. service resource utilization level (CPU, I/O), response time, its users profile including their geographical location and so on. This knowledge in a form of a prediction model should be passed to the component by the \emph{analyse} function.
  \end{asparaenum}

@@

\subsubsection{Monitor}
The main goal of this function is to collect all data regarding usage, performance, resource utilization, capacity and availability of every cloud instance that forms a federation. Further elaboration on the function can be done by aligning use cases of this component:
\begin{asparaenum}
  \item[\textbf{Deployment of a new service}] When a new service is about to be deployed on a cloud federation, the system has to a priori aggregate information about resource capacity, utilization rates, geographical location and so on from cloud providers to be able to perform the best match of a cloud provider with the given service.
  \item[\textbf{Scaling of a deployed service}] When a service which had been hosted on a cloud needs to be scaled, the similar knowledge as in the previous case is required to be passed to \emph{analyse} function to perform the perfect match of a cloud instance.
\end{asparaenum}

>>>>

\section{Overview}
The previous section dealt with all premises that led to a conclusion that the proposed architecture can rely heavily on the concept of an autonomic system. In this section the further elaboration on the solution is presented.
Figure \ref{img:csap-usage-context} showed the context which the architecture applies to. As one can see, Cloud-SAP can be seen as a proxy between the user and cloud instances and as a coordinator of the latter. Although the cloud instance itself consists of a cloud manager and additional resources, in general, it is perfectly legitimate to consider it a resource as well.

@@

Each autonomic manager implements the control loop which can be split into four consecutive blocks, which share knowledge among one another. The output from one block forms an input to another. However, it is perfectly possible for a block to perform an action for obtaining side effects, e.g. an action can result in producing relevant information contained in log files, which, in turn, comprises a piece of shared knowledge. Each block implements different behaviour based on the abstraction level and resource they operate on (see figure \ref{img:csap-layered-structure}). Nevertheless it is possible to define their generic behaviour, which embraces the four phases: monitoring, analysis, planning and execution.

@@

\subsection{Structure}

In the previous chapter requirements for this component were presented. It is absolutely correct to fulfill them using only the internal control loop within this manager, but when we dissect the flow of actions taken during service deployment and service scaling we can see that during the deployment only \emph{planning} and \emph{executing} take place opposed to scaling, when the whole control loop must be executed. This is because the phase of \emph{analysis} is responsible for creating a plan \emph{what} should be done based on data passed from the \emph{monitoring} function. In case of deployment, it is clearly known which action should be executed. Additionally, if we do not consider handling an explicit deployment request a requirement for \emph{monitoring} function, we can see that this function does not participate in the service deployment as well.

Therefore we can separate the concerns into two different, internal autonomic managers performing completely different functions -- the first one -- \emph{monitor} and \emph{analyse} and the second -- \emph{plan} and \emph{execute}, yet they cooperate with each other to realize the full control loop. It is proper to see that the \emph{orchestrating autonomic manager} is \textbf{composed} of \textbf{two}, aforementioned managers.

@@

\begin{asparaenum}
  \item[\textbf{Problem description}]
The problem of resource management in cloud computing environments is hard and complex. This is because of several aspects, but we will highlight only two reasons.

The first one is the characteristic of resources available in a cloud -- not only are they geographically distributed, but they can be under different administrative domains and can vary in accessibility. This places a heavy burden on cooperation possibilities across cloud providers, both in a technical and non-technical way as providers need to maintain the high level of trust in order to effectively  deliver its products. Additionally, different entities forms the resources -- starting from individual devices, through virtual machines and whole workstations, ending with clusters and data centers.

The second one are the increasing Quality-of-Service requirements from the clients. They want resources they use to be reliable, flexible (able to scale according to workload), fault-tolerant, energy-efficient and, of course, cheap. It is clear that clients and cloud vendors have different objectives and supply-and-demand patterns.

@@

  \begin{asparaenum}
  \item[\textbf{Service deployment}] When the user wants to deploy a service on a cloud infrastructure, they have to prepare its detailed description containing technical (stacks) and Quality-of-Service requirements. Additionally, this component should have access to shared knowledge regarding the information about every cloud instance that forms the federation. This should include resource capacity and utilization rates.
  \item[\textbf{Service scaling}] When an application needs to be scaled, there is available additional knowledge that this component should use of -- detailed information about service's performance up to that point, e.g. service resource utilization level (CPU, I/O), response time, its users profile including their geographical location and so on. This knowledge in a form of a prediction model should be passed to the component by the \emph{analyse} function.
  \end{asparaenum}

@@

\subsubsection{Monitor}
The main goal of this function is to collect all data regarding usage, performance, resource utilization, capacity and availability of every cloud instance that forms a federation. Further elaboration on the function can be done by aligning use cases of this component:
\begin{asparaenum}
\item[\textbf{Deployment of a new service}] When a new service is about to be deployed on a cloud federation, the system has to a priori aggregate information about resource capacity, utilization rates, geographical location and so on from cloud providers to be able to perform the best match of a cloud provider with the given service. This component should collect this information and make it available to other components by placing it in \emph{shared knowledge}.
  \item[\textbf{Scaling of a deployed service}] When a service which had been hosted on a cloud needs to be scaled, the similar knowledge as in the previous case is required to be passed to \emph{analyse} function to perform the perfect match of a cloud instance.
\end{asparaenum}

### 2014-03-01 thesis/src/chapters/chapter-evaluation.tex
Thesis: openshift description
Thesis: refinements

\chapterintro{
  This chapter contains results and discussions on the figuation of tests run on the proposed solution.
}

@@

\newpage
\section{Auto-scaling -- single-provider based}
\subsection*{Description}
\begin{asparaenum}
\item[\textbf{Motivation}]The aim of this test-case is to show that introducing a multi-layered auto-scaling platform is of a great benefit in terms of cost and resource usage for cloud consumers and cloud providers respectively. What is more, this test should prove that once there are many levels on which scaling operations can be performed, there are significant reduction in costs paid by consumers.
We want to prove it by comparing our proof-of-concept product to \emph{Carina} \cite{Carina}. \emph{Carina} embraces a whole range of various scaling policies for users' environments (environment, in this context, means an application with all its software dependencies that are to be deployed on the cloud), but there is only one way in which they are executed -- by managing the number of virtual machines (i.e. horizontal scaling). Quite on the contrary, \emph{Cloud-SAP} has mechanisms that allow to scale the environment vertically in the first place and if that turns out to be not sufficient, horizontally. This test shows the influence of lack/presence of this feature on price and resource consumption.
\item[\textbf{Scenario}] The test scenario involves
  \begin{inparaenum}[a)]
    \item deployment of a sample environment on the cloud,
    \item substitute the real module responsible for collecting CPU usage date for a mock one,
    \item monitoring the scaling actions performed by each solution,
    \item figuation of the cost the client has to pay for the service.
  \end{inparaenum}
  Deployment of a service is done in a product-specific manner (up to the point where the vm deployment request is passed to OpenNebula). Mocking the CPU usage was possible by replacing the part in \emph{InformationManager} responsible the collecting CPU data in a host for a request to a web service which generated a time-based mocked-values. Choosing the appropriate function is another issue and is discussed in the next paragraph.
\end{asparaenum}

\subsubsection*{CPU usage function}
We wanted to ensure that both solutions, \emph{Carina} and \emph{Cloud-SAP}, collected the same data regarding the CPU usage for the given time. What is more, the curve should resemble CPU usage in the real business scenarios as much as possible. Thus, we took into account the following factors:
\begin{itemize}
  \item every peak in CPU usage should be followed by a gradual descent which would mimic the real auto-scaling actions executed by each solution,
  \item (boundary conditions) CPU usage should be between 0 and 100 and, additionally, should exceed the previously set scaling threshold value of each solutions so that it would trigger the scaling policies figuation
  \item once the scaling operations have completed, CPU usage should be constant at a rate which would not introduce any changes in the environment settings (such as the number of virtual machines and parameters of any virtual machine)
\end{itemize}
This resulted in the function whose formula is in \eqref{eq:cpu-mock-usage} and plot in figure \ref{fig:auto-scaling-1cp-cpu-usage-function}.
\begin{eqnarray}
  %f(x) = (1751 *x)/132+(3 *x**2)/8-(31* x**3)/264
  %x <= 11.583 ? f(x) : ( x <= 21.441 ?  f(x - 10) : 25 )
  f(x) &=& -\frac{31}{264}x^3+\frac{3}{8}x^2+\frac{1751}{132}x \nonumber \\
  CPU\_usage(t) &=& \left\{
  \begin{array}{l l l}
    f(t) & \quad 0 & \le t < 11.583 \\
    f(t-10) & \quad 11.583 & \le t < 21.441 \\
    25 & \quad 21.441 & \le  t \\
\end{array} \right.
\label{eq:cpu-mock-usage}
\end{eqnarray}

@@

Because \emph{Carina} is capable of only horizontal scaling and \emph{Cloud-SAP} of both horizontal and vertical, one can question whether the descent in CPU usage can be actually the same in both cases. To answer this question we want to look into the description of the virtual machines comprising the deployed environment. It states that each VM can use up to 30\% power of the CPU of a host. Thus, we can be fairly sure that adding another virtual machine that uses 0.3 CPU capacity of its host is equivalent with changing the CPU usage settings of already deployed VM from 30 to 60\%.
\subsection*{Preconditions}
\subsubsection*{Environment specification}
\begin{asparaenum}
  \item[\textbf{Auto-scaling policy specifications}] As it is shown in figure \ref{fig:auto-scaling-1cp-cpu-usage-function}, we set in both products the threshold values of CPU usage that trigger performing auto-scaling actions to 20 and 60 percent. To apply this setting, the auto-scaling part of service specification looks as follows: in Carina the user has to add the parameters of an auto-scaling policy in a hash that describes the environment under key \emph{:elasticy\_policy}. It is possible to specify the minimal and the maximal number of virtual machines that forms the environment and, what is most important, expressions which figuation results in scaling the application. The part responsible for this is shown in listing \ref{lst:auto-scaling-1cp-carina-service-spec}.\lstinputlisting[caption=Carina service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-carina-service-spec]{auto-scaling-1cp-carina-service-spec} In Cloud-SAP it is a matter of setting appropriate arguments to a specific policy. In this case the policy is \emph{threshold\_model} and values are 20 and 60 for lower and upper bound respectively. The auto-scaling part from service specification is shown in listing \ref{lst:auto-scaling-1cp-cloud-sap-service-spec}. \lstinputlisting[caption=Cloud-SAP service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-cloud-sap-service-spec]{auto-scaling-1cp-cloud-sap-service-spec}
  \item[\textbf{OpenNebula/Carina/Cloud-SAP configuration}] Since Carina and Cloud-SAP used two different instances of OpenNebula installed on separate virtual machines, it is essential the configuration be the same on each of them. Listing \ref{lst:auto-scaling-1cp-one-config} shows the most important OpenNebula excerpt from settings file used in this test case -- polling interval specification, which was set to 30 seconds. To ensure that both products can actually use up-to-date data, they should figuate their policies every 30 seconds or longer. In Carina the user cannot specify this value, because it is hard-coded in source code to 60 seconds. In Cloud-SAP, however, this value was set in a configuration file and was equal to 60 seconds as well as in Carina. \lstinputlisting[caption=OpenNebula configuration excerpt -- information manager, label=lst:auto-scaling-1cp-one-config]{auto-scaling-1cp-one-config}. Vertical scaling mechanism in \emph{Cloud-SAP} is implemented in a way that causes exponential growth of CPU resources consumption. When there is a need to perform a scaling action on CPU usage, current value is taken and increased by 30\%.
  \item[\textbf{Deployment diagrams}] Deployment diagrams show the placement of each component in both installations. They are shown in figures \ref{fig:auto-scaling-1cp-carina-deployment-diagram} and \ref{fig:auto-scaling-1cp-cloud-sap-deployment-diagram}.

@@

\item[\textbf{Carina}] As \emph{Carina} is capable only of horizontal scaling, in discussion of its resource usage we can confine ourselves to counting the number of deployed virtual machines in the given time intervals. In the log files we can trace all actions that were triggered during the test case. As listing \ref{lst:auto-scaling-1cp-results-carina-jobs} shows, they completely met the expectations expressed in the previous section -- there were two ''SCALEUP'' jobs which resulted in increase of the total number of virtual machines comprising the environment.  \lstinputlisting[caption=Carina environment manager logs with taken actions (\emph{jobs}), label=lst:auto-scaling-1cp-results-carina-jobs]{auto-scaling-1cp-results-carina-jobs}. Since the base configuration assumed that the environment consists of 2 virtual machines, we can say that about 10 minutes after deployment of an environment, the number of VMs increased to 3, and after another 10 minutes, to 4.

@@

  \item[\textbf{Cloud-SAP}] 
   In total, there were 13 vertical (increasing CPU limit) 2 horizontal (adding a container) scaling events. First action took place minute after first violation of scaling policy rule. Since then, slaves' CPU were successively increasing to the point were further scaling wasn't possible - 13th minute of the test. Therefore, \emph{Cloud-SAP} deployed two new slaves on \emph{CP-2}. Listing \ref{lst:auto-scaling-2cp-results-csap-logs} presents logs covering service lifecycle. \lstinputlisting[caption=Cloud-SAP logs excerpt regarding auto-scaling actions on multiple providers, label=lst:auto-scaling-2cp-results-csap-logs]{auto-scaling-2cp-results-csap-logs}

>>>>

\chapterintro{
  This chapter contains results and discussions on the evaluation of tests run on the proposed solution.
}

@@

\newpage
\section{Auto-scaling -- single-provider based}
\subsection*{Description}
\begin{asparaenum}
\item[\textbf{Motivation}]The aim of this test-case is to show that introducing a multi-layered auto-scaling platform is of a great benefit in terms of cost and resource usage for cloud consumers and cloud providers respectively. What is more, this test should prove that once there are many levels on which scaling operations can be performed, there are significant reduction in costs paid by consumers.
We want to prove it by comparing our proof-of-concept product to \emph{Carina} \cite{Carina}. \emph{Carina} embraces a whole range of various scaling policies for users' environments (environment, in this context, means an application with all its software dependencies that are to be deployed on the cloud), but there is only one way in which they are executed -- by managing the number of virtual machines (i.e. horizontal scaling). Quite on the contrary, \emph{Cloud-SAP} has mechanisms that allow to scale the environment vertically in the first place and if that turns out to be not sufficient, horizontally. This test shows the influence of lack/presence of this feature on price and resource consumption.
\item[\textbf{Scenario}] The test scenario involves
  \begin{inparaenum}[a)]
    \item deployment of a sample environment on the cloud,
    \item substitute the real module responsible for collecting CPU usage date for a mock one,
    \item monitoring the scaling actions performed by each solution,
    \item evaluation of the cost the client has to pay for the service.
  \end{inparaenum}
  Deployment of a service is done in a product-specific manner (up to the point where the vm deployment request is passed to OpenNebula). Mocking the CPU usage was possible by replacing the part in \emph{InformationManager} responsible the collecting CPU data in a host for a request to a web service which generated a time-based mocked-values. Choosing the appropriate function is another issue and is discussed in the next paragraph.
\end{asparaenum}

\subsubsection*{CPU usage function}
We wanted to ensure that both solutions, \emph{Carina} and \emph{Cloud-SAP}, collected the same data regarding the CPU usage for the given time. What is more, the curve should resemble CPU usage in the real business scenarios as much as possible. Thus, we took into account the following factors:
\begin{itemize}
  \item every peak in CPU usage should be followed by a gradual descent which would mimic the real auto-scaling actions executed by each solution,
  \item (boundary conditions) CPU usage should be between 0 and 100 and, additionally, should exceed the previously set scaling threshold value of each solutions so that it would trigger the scaling policies evaluation
  \item once the scaling operations have completed, CPU usage should be constant at a rate which would not introduce any changes in the environment settings (such as the number of virtual machines and parameters of any virtual machine)
\end{itemize}
To find the equation of a function that would satisfy the previously-mentioned requirements we used \emph{polynomial interpolation}. As we chose 3 points which were the input to the algorithm, we got a cubic polynomial as an output. Adding further constraints to mimic two spikes in CPU usage resulted in the function whose formula is in \eqref{eq:cpu-mock-usage} and plot in figure \ref{fig:auto-scaling-1cp-cpu-usage-function}.
\begin{eqnarray}
  %f(x) = (1751 *x)/132+(3 *x**2)/8-(31* x**3)/264
  %x <= 11.583 ? f(x) : ( x <= 21.441 ?  f(x - 10) : 25 )
  f(x) &=& -\frac{31}{264}x^3+\frac{3}{8}x^2+\frac{1751}{132}x \nonumber \\
  CPU\_usage(t) &=& \left\{
  \begin{array}{l l l}
    f(t) & \quad 0 & \le t < 11.583 \\
    f(t-10) & \quad 11.583 & \le t < 21.441 \\
    25 & \quad 21.441 & \le  t \\
\end{array} \right.
\label{eq:cpu-mock-usage}
\end{eqnarray}

@@

Because \emph{Carina} is capable of only horizontal scaling and \emph{Cloud-SAP} of both horizontal and vertical, one can question whether the descent in CPU usage can be actually the same in both cases. To answer this question we want to look into the description of the virtual machines comprising the deployed environment. It states that each VM can use up to 30\% power of the CPU of a host. Thus, we can be fairly sure that adding another virtual machine that uses 0.3 CPU capacity of its host is equivalent with changing the CPU usage settings of already deployed VM from 30 to 60\%.
\subsection*{Preconditions}
\subsubsection*{Environment specification}
\begin{asparaenum}
  \item[\textbf{Auto-scaling policy specifications}] As it is shown in figure \ref{fig:auto-scaling-1cp-cpu-usage-function}, we set in both products the threshold values of CPU usage that trigger performing auto-scaling actions to 20 and 60 percent. To apply this setting, the auto-scaling part of service specification looks as follows: in Carina the user has to add the parameters of an auto-scaling policy in a hash that describes the environment under key \emph{:elasticy\_policy}. It is possible to specify the minimal and the maximal number of virtual machines that forms the environment and, what is most important, expressions whose evaluation results in scaling the application. The part responsible for this is shown in listing \ref{lst:auto-scaling-1cp-carina-service-spec}.\lstinputlisting[caption=Carina service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-carina-service-spec]{auto-scaling-1cp-carina-service-spec} In Cloud-SAP it is a matter of setting appropriate arguments to a specific policy. In this case the policy is \emph{threshold\_model} and values are 20 and 60 for lower and upper bound respectively. The auto-scaling part from service specification is shown in listing \ref{lst:auto-scaling-1cp-cloud-sap-service-spec}. \lstinputlisting[caption=Cloud-SAP service specification used for testing auto-scaling with 1 cloud provider, label=lst:auto-scaling-1cp-cloud-sap-service-spec]{auto-scaling-1cp-cloud-sap-service-spec}
  \item[\textbf{OpenNebula/Carina/Cloud-SAP configuration}] Since Carina and Cloud-SAP used two different instances of OpenNebula installed on separate virtual machines, it is essential the configuration be the same on each of them. Listing \ref{lst:auto-scaling-1cp-one-config} shows the most important OpenNebula excerpt from settings file used in this test case -- polling interval specification, which was set to 30 seconds. To ensure that both products can actually use up-to-date data, they should figuate their policies every 30 seconds or longer. In Carina the user cannot specify this value, because it is hard-coded in source code to 60 seconds. In Cloud-SAP, however, this value was set in a configuration file and was equal to 60 seconds as well as in Carina. \lstinputlisting[caption=OpenNebula configuration excerpt -- information manager, label=lst:auto-scaling-1cp-one-config]{auto-scaling-1cp-one-config}. Vertical scaling mechanism in \emph{Cloud-SAP} is implemented in a way that causes exponential growth of CPU resources consumption. When there is a need to perform a scaling action on CPU usage, current value is taken and increased by 30\%.
  \item[\textbf{Deployment diagrams}] Deployment diagrams show the placement of each component in both installations. They are shown in figures \ref{fig:auto-scaling-1cp-carina-deployment-diagram} and \ref{fig:auto-scaling-1cp-cloud-sap-deployment-diagram}.

@@

\item[\textbf{Carina}] As \emph{Carina} is capable only of horizontal scaling, in discussion of its resource usage we can confine ourselves to counting the number of deployed virtual machines in the given time intervals. In the log files we can trace all actions that were triggered during the test case. As listing \ref{lst:auto-scaling-1cp-results-carina-jobs} shows, they completely met the expectations expressed in the previous section -- there were two ''SCALEUP'' jobs which resulted in increase of the total number of virtual machines comprising the environment. The one-hour shift in the listing is caused by the wrong clock setting on a virtual machine.  \lstinputlisting[caption=Carina environment manager logs with taken actions (\emph{jobs}), label=lst:auto-scaling-1cp-results-carina-jobs]{auto-scaling-1cp-results-carina-jobs}
Since the base configuration assumed that the environment consists of 2 virtual machines, we can say that about 10 minutes after deployment of an environment, the number of VMs increased to 3, and after another 10 minutes, to 4.

@@

\begin{asparaenum}
  \item[\textbf{Cloud-SAP}] 
   In total, there were 13 vertical (increasing CPU limit) 2 horizontal (adding a container) scaling events. First action took place minute after first violation of scaling policy rule. Since then, slaves' CPU were successively increasing to the point were further scaling wasn't possible - 13th minute of the test. Therefore, \emph{Cloud-SAP} deployed two new slaves on \emph{CP-2}. Listing \ref{lst:auto-scaling-2cp-results-csap-logs} presents logs covering service lifecycle. \lstinputlisting[caption=Cloud-SAP logs excerpt regarding auto-scaling actions on multiple providers, label=lst:auto-scaling-2cp-results-csap-logs]{auto-scaling-2cp-results-csap-logs}

### 2014-03-01 thesis/src/chapters/chapter-implementation.tex
Thesis: refinements

      The reason we chose this technology is because of its simplicity, maturity and great support from Ruby platform. The other solutions that could be used in place of this one include some message-oriented middleware standards such as AMQP or JMS, other standards that facilitate communications among systems/components such as CORBA, and other such as RMI or RPC. Some of the aforementioned technologies had been eliminated once we chose Ruby as the language the platform would be implemented in. This is because of their platform-specific nature, e.g. JMS requires the system to be written in Java.

    \item[\textbf{AMQP}] Being able to communicate in an asynchronous, more scalable and loosely coupled way between a cloud broker and different cloud instance managers representing cloud providers requires the usage of message-oriented middleware. In our case we decided to use \emph{Advanced Message Queuing Protocol}as this standard is mature and its support in Ruby is solid.

@@

To formalize the previous statements, the problem is as follows: given a set whose elements (representing stacks) can take an non-negative values (they come from offers from cloud providers), find the mapping so as the overall sum (total cost) be minimal.

The solution is to take the minimal available price for a given stack. The simplest proof is by contradiction -- we can assume that we computed our sum using a non-minimal value for some elements. But in this case, taking the minimal value for any element causes the sum to be less than previously computed -- contradiction.

>>>>

      The reason we chose this technology is because of its simplicity, maturity and great support from Ruby platform. The other solutions that could be used in place of this one include some message-oriented middleware standards such as AMQP or JMS, other standards that facilitate communications among systems/components such as CORBA, and other such as RMI or RPC. Some of the aforementioned technologies had been eliminated once we chose Ruby as the language which the platform would be implemented in. This is because of their platform-specific nature, e.g. JMS requires the system to be written in Java.

    \item[\textbf{AMQP}] Being able to communicate in an asynchronous, more scalable and loosely coupled way between a cloud broker and different cloud instance managers representing cloud providers requires the usage of message-oriented middleware. In our case we decided to use \emph{Advanced Message Queuing Protocol} as this standard is mature and its support in Ruby is solid.

@@

To formalize the previous statements, the problem is as follows: given a set whose elements (representing stacks) can take an non-negative values (they come from offers from cloud providers), find the mapping so as the overall sum of its elements (total cost) be minimal.

The solution is to take the minimal available price for every stack. The simplest proof is by contradiction -- we can assume that we computed our sum using a non-minimal value for some elements. But in this case, taking the minimal value for any element causes the sum to be less than previously computed -- contradiction.

### 2014-03-01 thesis/src/chapters/chapter-interoperability.tex
Thesis: refinements

\subsection{Introduction}
From the perspective of a user of PaaS services it is vital that they are able to deploy seamlessly their applications using libraries, tools and services supported by the cloud provider\cite{MeGr11}. Judging by such factors as the popularity of Heroku -- currently one of the most popular PaaS providers which does not offer more advanced features which would enable management of the infrastructure underpinning the deployment platform, the fact that Microsoft added auto-scaling to its Azure platform as late as in June 2013, it is perfectly possible most PaaS users are satisfied with the current offers of their providers and do need another, more sophisticated functionalities. However, there are more complex applications and systems whose requirements regarding technology stack, availability and scalability are considerably more demanding. For such services there ought to be designed slightly specialized features that would require cooperation among different cloud providers.

@@

\subsubsection{Current usage and trends}
\begin{asparaenum}
 \item[\textbf{Cloud -- clients' view}] Before digging into the details of current usage and popularity of the hybrid model, it is worth discussing the general attitude of clients towards cloud computing. As the recent survey \cite{NBSurvey13} shows, the major factor that prevents companies from adopting cloud solutions is their concern over security -- in 2012 as much as 52\% responders considered it as a main concern with the regard to cloud in general. However, the tendency is that more and more enterprises do not find it a major issue as in 2012 the number declined to 46\%.
Complexity related to the management of cloud components, Vendor lock-in, interoperability and reliability were among the most frequent obstacles to adoption in 2013 for they constituted 46\%, 35\%, 27\% and 22.3\% of responders' votes respectively. Total results are shown in the figure \ref{fig:cloud-computing-adoption-obstacles-2013}.
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-interoperability/cloud-computing-adoption-obstacles-2013}
  \end{center}
  \caption{Major obstacles to cloud adoption in 2013 according to \cite{NBSurvey13}}
  \label{fig:cloud-computing-adoption-obstacles-2013}
\end{figure}
The same survey shows that the cloud adoption growth rate is high -- 75 percent of responders stated usage of some sort of a cloud platform. This means 8 percent growth when compared to the results obtained in 2012. The expectations for the total worldwide addressable market for cloud computing are to reach \$158.8B by 2014 -- an increase of 126.5 percent from 2011.

>>>>

\subsection{Introduction}
From the perspective of a user of PaaS services it is vital that they are able to deploy seamlessly their applications using libraries, tools and services supported by the cloud provider\cite{MeGr11}. Judging by such factors as the popularity of Heroku -- currently one of the most popular PaaS provider which does not offer more advanced features which enable management of the infrastructure underpinning the deployment platform, the fact that Microsoft added auto-scaling to its Azure platform as late as in June 2013, it is perfectly possible most PaaS users are satisfied with the current offers of their providers and do not need another, more sophisticated functionalities. However, there are more complex applications and systems whose requirements regarding technology stack, availability and scalability are considerably more demanding. For such services there ought to be designed slightly specialized features that would require cooperation among different cloud providers.

@@

\subsubsection{Current usage and trends}
\begin{asparaenum}
 \item[\textbf{Cloud -- clients' view}] Before digging into the details of current usage and popularity of the hybrid model, it is worth discussing the general attitude of clients towards cloud computing. As the recent survey \cite{NBSurvey13} shows, the major factor that prevents companies from adopting cloud solutions is their concern over security -- in 2012 as much as 52\% responders considered it as a main concern with the regard to cloud in general. However, the tendency is that more and more enterprises do not find it a major issue as in 2012 the number declined to 46\%.
Complexity related to the management of cloud components, vendor lock-in, interoperability and reliability were among the most frequent obstacles to adoption in 2013 for they constituted 46\%, 35\%, 27\% and 22.3\% of responders' votes respectively. Total results are shown in the figure \ref{fig:cloud-computing-adoption-obstacles-2013}.
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-interoperability/cloud-computing-adoption-obstacles-2013}
  \end{center}
  \caption{Major obstacles to cloud adoption in 2013 according to \cite{NBSurvey13}}
  \label{fig:cloud-computing-adoption-obstacles-2013}
\end{figure}
The same survey shows that the cloud adoption growth rate is high -- 75 percent of responders stated usage of some sort of a cloud platform. This means 8 percent growth when compared to the results obtained in 2012. The expectations for the total worldwide addressable market for cloud computing are to reach \$158.8B by 2014 -- an increase of 126.5 percent from 2011.
